A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
improvements of "Southern Scandinavia"

`r a("Southern Scandinavia")`:
The region *Southern Scandinavia* includes all of Denmark with Jutland, Funen, Zeeland and all smaller islands as well as large parts of the east of southern Sweden, and coastal regions in Schleswig-Holstein and Mecklenburg-Western Pomerania. The ^14^C data are very well distributed across Jutland, Funen and the Swedish Skåne region. Since the Bronze Age in Scandinavia begins much later than in Central Europe and is measured by another chronological system, the diachronic developments cannot simply be compared by means of the tripartite structure of the Early, Middle and Late Bronze Ages. The majority of data from Scandinavia are from the period IB onwards. In this respect, the data density for almost the entire Bronze Age is good -- also with regard to the two variables *burial type* and *burial construction*. The Late Neolithic from 2200calBC is a desideratum -- although at a higher level than, for example, the Early Bronze Age in *Northeastern France*. The adjustment in Figure \@ref(fig:development-proportions-regions-pseudoquant) is difficult, since the period which is labeled with Early Bronze Age due to the situation in Central Europe actually corresponds to the local Late Neolithic. If one carries out the resulting mental shift -- the Central European Middle Bronze Age corresponds to the Nordic Early Bronze Age -- and then compares the proxy of the relative grave form development with the archaeological observations, then one finds a solid agreement: body graves were the rule in periods I and II (about 1800-1300calBC), but cremations also occurred sporadically. From period III onwards cremation burials gained the upper hand. In the Scandinavian Early Bronze Age (i.e. Middle Bronze Age in Figure \@ref(fig:development-proportions-regions-pseudoquant)) burials in burial mounds were the absolute rule. In the Late Bronze Age, shallow burial fields were added.

>>>>

`r a("Southern Scandinavia")`:
The region *Southern Scandinavia* includes all of Denmark with Jutland, Funen, Zeeland and all smaller islands as well as large parts of the east of southern Sweden, and coastal regions in Schleswig-Holstein and Mecklenburg-Western Pomerania. The ^14^C data are very well distributed across Jutland, Funen and the Swedish Skåne region. Since the Bronze Age in Scandinavia begins much later than in Central Europe and is measured by another chronological system, the diachronic developments cannot simply be compared by means of the tripartite structure of the Early, Middle and Late Bronze Ages. The period which is labeled Early Bronze Age due in Central Europe actually corresponds to the Scandinavian Late Neolithic. The majority of data from Scandinavia are from the period IB onwards. In this respect, the data density for almost the entire Bronze Age is good -- also with regard to the two variables *burial type* and *burial construction*. The Late Neolithic from 2200calBC is a desideratum. If one carries out the necessary mental shift -- the Central European Middle Bronze Age corresponds to the Nordic Early Bronze Age -- and then compares the proxy of the relative grave form development with the archaeological observations, then one finds a solid agreement: body graves were the rule in periods I and II (about 1800-1300calBC), but cremations also occurred sporadically. From period III onwards cremation burials gained the upper hand. In the Scandinavian Early Bronze Age burials in burial mounds were the absolute rule. In the Late Bronze Age, flat burial fields were added.
